Wavelet Spatio-Temporal Change Detection on multi-temporal SAR images

### 2021-11-17 tex/paper.wecs/wecs_tgrs__trans16nov21.tex
ajustes (17nov21)

@@

\author{Rodney~V.~Fonseca, Rog\'{e}rio~G.~Negri,
        Alu\'{i}sio~Pinheiro,
        and~Abdourrahmane~Atto,~\IEEEmembership{Senior~Member,~IEEE}% <-this % stops a space
\thanks{This work was supported by FAPESP grants 2016/24469-6 and 2018/04654-9 and CNPq grants 309230/2017-9 and 310991/2020-0.}
\thanks{R.~Fonseca and A.~Pinheiro are with the Department of Statistics, University of Campinas, Campinas 13083-859, Brazil (e-mails: ra192588@dac.unicamp.br; pinheiro@ime.unicamp.br).}
\thanks{A.~Atto is with the LISTIC - Polytech Annecy-Chamb\'{e}ry, Universit\'{e} de Savoie, 74944 Annecy le Vieux Cedex, France (e-mail: Abdourrahmane.Atto@univ-savoie.fr).}
\thanks{R.~G.~Negri is with the Department of Environmental Engineering, São Paulo State University, São José dos Campos, Brazil (e-mail: rogerio.negri@unesp.br).}
}
% <-this % stops a space
%\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}

@@

@@

Let $\mathcal{I}^{(1)},\ldots,\mathcal{I}^{(n)}$ be a set of matrices representing the images of some region of interest and $n$ instants in time. These images may be relative to one SAR channel or a combination of channels; this will be specified when appropriate. Our goal is twofold: to find possible points in time where some relevant changes might have taken place at the region represented in $\mathcal{I}^{(m)}$, $m=1,\ldots,n$, and to find which regions are closely associated to the observed changes along time. We shall address these tasks by analyzing the bidimensional stationary discrete wavelet decomposition of $\mathcal{I}^{(m)}$. Stationary wavelets (also known as non-decimated or redundant wavelets) is a traditional de-noising method that can be efficiently applied to two-dimensional signals such as images \cite{coifman1995translation,atto2012multidate,atto2016wavelet}. After application of this wavelet transform to $\mathcal{I}^{(m)}$ at some appropriate resolution level $J\geq 1$, one of its by-products is a matrix of so called approximation wavelet coefficients $\vX^{(m)}$, a smooth version of $\mathcal{I}^{(m)}$ with the same dimension. The higher $J\in\{1,\ldots,\log_2(k)\}$ is, the smoother $\vX^{(m)}$ gets, where $k$ is the minimum between the numbers of rows and columns of $\mathcal{I}^{(m)}$. Many other aspects can be involved in wavelet analysis of images (e.g., different types of wavelet transform, choice of wavelet basis, thresholding of detail coefficients, etc.), but in the current work we focus on $\vX^{(m)}$, which provides a simple way of performing wavelet smoothing and that gives interesting results; extensions based on further aspects of wavelet transforms are straightforward.

We can then consider further apportioning the total $\mathbb{L}_2$ energy of $\left\{\vX^{(m)}\right\}$ as
\begin{equation} 
\sum_{m=1}^n\|\vX^{(m)}\|^2 = n\|\bar{\mathcal{I}}\|^2+2n\langle\bar{\vX}-\bar{\mathcal{I}},\bar{\mathcal{I}}\rangle+\sum_{m=1}^n\|\mathcal \vX^{(m)}-\bar{\mathcal{I}}\|^2,\label{E:eq_ANOVAlogimage}
\end{equation}
where $\bar{\mathcal{I}}=n^{-1}\sum_{m=1}^n\mathcal{I}^{(m)}$, $\bar{\vX}=n^{-1}\sum_{m=1}^n\vX^{(m)}$ and $\|\vA\|^2=\sum_{i=1}^n\sum_{j=1}^m a_{ij}^2$ for a $n\times m$ matrix $\vA=[a_{ij}]$. The last term in (\ref{E:eq_ANOVAlogimage}) measures deviations in time of $\vX^{(m)}$ compared to an {\it average image} $\bar{\mathcal{I}}$, what motivates us to such deviations to detect change points in time. Since each element (pixel) in $\vX^{(m)}$ also has a corresponding sequence of deviations in time, the relation of each local deviation to the overall measure can also be quantified, what allows us to detect changes in space. Such relation shall be computed in the present work with the Pearson correlation, what shares connections with the idea of feature screening employed in high-dimensional regression, as explained further. Other measures of change in time could be evaluated as well, such as squared differences of consecutive times $\|\mathcal \vX^{(m)}-\vX^{(m-1)}\|^2$, $d(\vX^{(m)},\bar{\vX})$ with $d(\cdot,\cdot)$ denoting some distance measure (e.g., Hellinger, Kullback-Leibler, etc.), among many other possibilities.

Let $X_{k,l}^{(m)}$ and $\bar{\mathcal{I}}_{k,l}$ be the entry $(k,l)$ of $\vX^{(m)}$ and $\bar{\mathcal{I}}$, respectively. Computing $D_{k,l}^{(m)}=(X_{k,l}^{(m)}-\bar{\mathcal{I}}_{k,l})^2$, we denote the matrix of squared mean differences as $\vD^{(m)} = [D_{k,l}^{(m)}]$. We then 
analyze the time series given by
\begin{equation} 
\vd(m)= \sum_{k,l}D_{k,l}^{(m)} = \sum_{k,l}(X_{k,l}^{(m)} - \bar{\mathcal{I}}_{k,l})^2,
\label{E:eq_defdm}
\end{equation}
$m=1,\ldots,n$, which measure the temporal overall variation with respect to $\bar{\mathcal{I}}$.

The time points with highest values of $\vd(m)$ represent the images for which the most expressive changes take place, where changes here are measured through $\mathbb{L}_2$ energy. Define the  $n\times p$ matrix
\begin{equation*}
 \vD=\left(
 \begin{array}{c}
 vec(\vD^{(1)})^T\\
 \vdots\\
 vec(\vD^{(n)})^T\\
 \end{array}
 \right),
\label{eq_defmatrixD}
\end{equation*}
where $vec(\vD^{(m)})$ is the $p\times 1$ vector of wavelet coefficients for time $m$ and $p=\#\{k,l\}$ is total number of locations represented by $\vX^{(m)}$, $m=1,\ldots,n$. Sparsity \cite{johnstone2009statistical} on wavelet coefficients plays a special role here.  We suppose a handful of coefficients drive the changes given by $\vd$, so that the effective dimension of $\vD$ (number of locations where relevant changes occur), say $s_d$, is such that $s_d<<p$. This can be represented as the following linear model
\begin{equation} 
\vd=\vD\vbeta+\vxi
\label{E:sparsemodel_d}
\end{equation}
where $\vbeta$ is sparse, i.e., it has $p-s_d$ null elements, and $\vxi^{(d)}$ is some $n\times 1$ random vector of errors.

In order to identify spatio-temporal changes, we employ the idea of ultra-high dimensional correlation screening \cite{fan2020statistical} as follows. For each local squared mean deviation time series, given by individual elements of $\vD^{(m)}$ across $m=1,\ldots,n$, consider the absolute value of its Pearson correlation with the overall squared mean deviations, given by $\vd$:
\begin{equation*}
R_{k,l}= |\corr\left( \vD_{k,l}, \vd\right)|,
\label{def_Rkld}
\end{equation*}
where $\vD_{k,l}=(D_{k,l}(1),\ldots,D_{k,l}(n))^T$ is the time series of squared mean deviations of wavelet coefficients for the two-dimensional index $\{k,l\}$.

@@

We have a matrix $\vR=[R_{k,l}]$ of correlations of ultra-high dimension. Define the set of 
{\it important} indices for changes in images with respect to $\bar{\mathcal I}$ as 
$\mathcal{M}^{*}=\{(k,l): \textit{changes in } \{\mathcal{I}^{(m)}\}_{m=1}^m \textit{ with respect to}$ $\bar{\mathcal{I}}$ \textit{are affected by changes in location corresponding to index} $(k,l)$ $\textit{in such images}\}$.  This set coincides with the non-zero vectorized one-dimensional indices for the sparse representation of $\vbeta$ in (\ref{E:sparsemodel_d}). 
We build the empirical set of indices flagged as corresponding to change locations by
\begin{equation}
\mathcal{M}_{\tau}=\{(k,l):|R_{k,l}|>\tau\},
\label{E:def_Mtaud}
\end{equation}
where $\tau_d>0$ is a convenient threshold value, function of $n$ and $J$. Under some regularity conditions, the probability that $\mathcal{M}_{\tau}$ contains its target set satisfies
\[
P(\mathcal{M}_{\tau}\supset\mathcal{M}^{*})\rightarrow 1,
\]
as $n\rightarrow\infty$ \cite{fan2020statistical}, where $P$ denotes a probability measure. In other words, the empirical set $\mathcal{M}_{\tau}$ has high probability of detecting the correct change locations in $\mathcal{M}^{*}$ when the number of observations $n$ is large.

Further geometrical motivation for our proposal is given as follows. As defined by (\ref{E:eq_defdm}), we expect $\vd$ to be a vector with some few high values, say $s_d$, and $n-s_d$ smaller values. This segregates the multi-temporal images, since the former time points identify the images in which significant changes occur, while the latter indices identify time points with no major changes. Consider $U>L>0$ such that the $s_d$ highest values of $\vd$ are larger than $U$, and the $n-s_d$ smallest values of $\vd$ are smaller than $L$. We also take $\delta=U-L$. The indices defined by  (\ref{E:def_Mtaud}) are such that   
\[
\frac{<\vD_{k,l},\vd>}{\|\vD_{k,l}\|_2\|\vd\|_2}>\tau,
\]
i.e., such that  $\sum_{m=1}^nD_{k,l}^{(m)}\vd(m)>\tau\|\vD_{k,l}\|_2\|\vd\|_2$. This can be rewritten as
\[
\left|\sum_{m:\vd(m)>U} D_{k,l}^{(m)}\right|-\left|\sum_{m:\vd(m)<L} D_{k,l}^{(m)}\right|>\Delta,
\]
for some arbitrary $\Delta>>0$ (which can be a function of $n$ and $J$). Thence, when we employ correlation screening we select the two-dimensional wavelet indices which have the closest empirical directions to the vector of image temporal changes. Thus we are performing a truly spatio-temporal change detection in a single procedure.

@@

\subfigure[Ground truth change/non-change samples]{\includegraphics[width=0.23\textwidth]{../../figs/coming-soon.png}\label{figImgSentinelROIs}}

>>>>

\usepackage{mathabx}

@@

\author{Rodney~V.~Fonseca, Rog\'{e}rio~G.~Negri,
        Alu\'{i}sio~Pinheiro,
        and~Abdourrahmane~Atto,~\IEEEmembership{Senior~Member,~IEEE}% <-this % stops a space
\thanks{This work was supported by FAPESP (Grants 2016/24469-6, 2018/04654-9, 2021/01305-6) and CNPq (Grants 309230/2017-9 and 310991/2020-0).}
\thanks{R.~Fonseca and A.~Pinheiro are with the Department of Statistics, University of Campinas, Campinas 13083-859, Brazil (e-mails: ra192588@dac.unicamp.br; pinheiro@ime.unicamp.br).}
\thanks{A.~Atto is with the LISTIC - Polytech Annecy-Chamb\'{e}ry, Universit\'{e} de Savoie, 74944 Annecy le Vieux Cedex, France (e-mail: Abdourrahmane.Atto@univ-savoie.fr).}
\thanks{R.~G.~Negri is with the Department of Environmental Engineering, São Paulo State University, São José dos Campos, Brazil (e-mail: rogerio.negri@unesp.br).}
}
% <-this % stops a space
%\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}

@@

\section{Theory Background}\label{section_theroy}

\textcolor{red}{Não seria interessante inserir uma breve secao abordando a questão de destaquei em vermelho mais adiante (sobre wavelet) assim como a definicao de feature screening, ultr-dimension, etc... Fazendo isso estaria preparando o terreno para as discussões que seguem.}

@@

%%%RGN: vou usar texto em azul para coisas a serem conversadas depois.

%Let $\mathcal{I}^{(1)},\ldots,\mathcal{I}^{(n)}$ be a set of matrices representing the images of some region of interest and $n$ instants in time.
Let $\mathcal{I}^{(1)},\ldots,\mathcal{I}^{(n)}$ be an image time series defined on a support $\mathcal{S} = \left\lbrace 1,\ldots,u  \right\rbrace \times \left\lbrace 1,\ldots,v  \right\rbrace \subset \mathbbm{N}^2$, hence representing a region of interest over $n$ distinct instants.
%
\textcolor{blue}{These images may be relative to one SAR channel or a combination of channels; this will be specified when appropriate}. Our goal is twofold: to find possible points in time where some relevant changes might have taken place at the region represented in $\mathcal{I}^{(m)}$, $m=1,\ldots,n$, and to find which regions are closely associated to the observed changes along time. We shall address these tasks by analyzing the bidimensional stationary discrete wavelet decomposition of $\mathcal{I}^{(m)}$. Stationary wavelets (also known as non-decimated or redundant wavelets) is a traditional de-noising method that can be efficiently applied to two-dimensional signals such as images \cite{coifman1995translation,atto2012multidate,atto2016wavelet}.

\textcolor{red}{Existe alguma formalizacao minima que poderia ser inserida aqui a fim de: (i) explicar como o método funciona; (ii) como X(m) origina deste processo; (iii) qual o significado do J neste contexto. A falta da ligacao entre o ponto de partida e as proximas formalizacoes deixa um pouco de duvidas. Se quiser, podemos fazer um texto bem compacto e um diagrama para simplificar.}

After application of this wavelet transform to $\mathcal{I}^{(m)}$ at some appropriate resolution level $J\geq 1$, one of its by-products is a matrix of so called approximation wavelet coefficients $\vX^{(m)}$, a smoothed version of $\mathcal{I}^{(m)}$ 
defined on the same support $\mathcal{S}$.
%with the same dimension. 
The higher $J\in\{1,\ldots,\log_2( \min{u,v} )\}$ is, the smoother $\vX^{(m)}$ gets. %, where $k$ is the minimum between the numbers of rows and columns of $\mathcal{I}^{(m)}$.

%Besides many other aspects can be involved in wavelet analysis of images (e.g., different types of wavelet transform, choice of wavelet basis, thresholding of detail coefficients, etc.), but in the current work we focus on $\vX^{(m)}$, which provides a simple way of performing wavelet smoothing and that gives interesting results; extensions based on further aspects of wavelet transforms are straightforward.
Beyond many other aspects that can be involved in wavelet analysis of images, which may include different types of wavelet transform and basis as well the use of thresholding for detail coefficients, the current construction is focused on $\vX^{(m)}$ to provide a simple wavelet smoothing. Nevertheless, extensions based on distinct aspects are straightforward.

We can then consider further apportioning the total $\mathbb{L}_2$ energy of the series $\left\{\vX^{(m)}\right\}_{m=1,\ldots,n}$ as:
\begin{equation}\label{E:eq_ANOVAlogimage}
\begin{split}
\sum_{m=1}^n\|\vX^{(m)}\|_F^2
= n\|\overline{\mathcal{I}}\|_F^2 + 2n\langle\overline{\vX}-\overline{\mathcal{I}},\overline{\mathcal{I}}\rangle + \\
+ \sum_{m=1}^n\|\mathcal \vX^{(m)} - \overline{\mathcal{I}}\|_F^2,
\end{split}
\end{equation}
where $\overline{\mathcal{I}}=n^{-1}\sum_{m=1}^n\mathcal{I}^{(m)}$ and $\overline{\vX}=n^{-1}\sum_{m=1}^n\vX^{(m)}$; $\| \cdot \|_F$ and $\left\langle \cdot , \cdot \right\rangle_F$ represents the Forbenius norm and inner product, respectively. Naturally, both $\overline{\mathcal{I}}$ and $\overline{\vX}$ shares the support $\mathcal{S}$.

% and $\|\vA\|^2=\sum_{i=1}^n\sum_{j=1}^m a_{ij}^2$ for a $n\times m$ matrix $\vA=[a_{ij}]$.

%\sum_{m=1}^n\|\vX^{(m)}\|^2 = n\|\bar{\mathcal{I}}\|^2+2n\langle\bar{\vX}-\bar{\mathcal{I}},\bar{\mathcal{I}}\rangle+\sum_{m=1}^n\|\mathcal \vX^{(m)}-\bar{\mathcal{I}}\|^2,

The most right-hand term in Equation~(\ref{E:eq_ANOVAlogimage}) measures the deviations 
between the wavelet coefficients at distinct instants ($\vX^{(m)}; \ m=1,\ldots,n$) regarding the \textit{average image} (i.e., $\overline{\mathcal{I}}$). Such deviations may favor detecting relevant changes over the time.
%us to such deviations to detect change points in time
%in time of $\vX^{(m)}$ compared to an {\it average image} $\overline{\mathcal{I}}$, what motivates us to such deviations to detect change points in time. 
%
Since each element (i.e., a pixel/position $(k,l)\in \mathcal{S}$) of $\vX^{(m)}$ also has a corresponding sequence of deviations in time, 
%the relation of each 
the local deviation to the overall measure 
%can also be quantified, what allows us to detect changes in space. 
may also allow detecting the spatial changes. 
%Such relation shall be computed in the present work with the Pearson correlation, what shares connections with the idea of feature screening employed in high-dimensional regression, as explained further. 
Among several approaches able to detect change events, the Pearson correlation coefficient rises as an convenient alternative. Furthermore, such measure \textcolor{blue}{shares connections with the idea of feature screening employed in high-dimensional regression, as explained further.}

%%%RGN: Desnecessario? (e pode confundir...)
%Other measures of change in time could be evaluated as well, such as squared differences of consecutive times $\|\mathcal \vX^{(m)}-\vX^{(m-1)}\|^2$, $d(\vX^{(m)},\bar{\vX})$ with $d(\cdot,\cdot)$ denoting some distance measure (e.g., Hellinger, Kullback-Leibler, etc.), among many other possibilities.

%%%RGN: vou remover a "," nos indices de posica para despoluir/descarregar  a notacão, ok?

Let $X_{kl}^{(m)}$ and $\overline{\mathcal{I}}_{kl}$ be the entry $(k,l)$ of $\vX^{(m)}$ and $\overline{\mathcal{I}}$, respectively. 
%
The matrix $\vD^{(m)}$ embraces the squared differences between $\vX^{(m)}$ and $\overline{\mathcal{I}}$, where $D_{kl}^{(m)} = \left( \vX_{kl}^{m} - \overline{\mathcal{I}}_{kl} \right)^2$.
%
Therefore, it is defined the temporal overall variation sequence $\left\lbrace \vd^{(m)}  \right\rbrace_{m=1,\ldots,n}$, whose elements are given by:
\begin{equation}\label{E:eq_defdm}
\vd(m)= \sum_{k=1}^{u} \sum_{l=1}^{v} D_{kl}^{(m)} %; \ m=1,\ldots,n
\end{equation}

%$X_{kl}^{(m)}$ and $\overline{\mathcal{I}}_{kl}$ at each position $(k,l)$ as 
%Computing $D_{kl}^{(m)}=(X_{k,l}^{(m)}-\bar{\mathcal{I}}_{k,l})^2$, we denote the matrix of squared mean differences as $\vD^{(m)} = [D_{k,l}^{(m)}]$. We then 
%analyze the time series given by
%\begin{equation} 
%\vd(m)= \sum_{k,l}D_{k,l}^{(m)} = \sum_{k,l}(X_{k,l}^{(m)} - \bar{\mathcal{I}}_{k,l})^2,
%\label{E:eq_defdm}
%\end{equation}
%$m=1,\ldots,n$, which measure the temporal overall variation with respect to $\bar{\mathcal{I}}$.

In this context, a instant $m$ in $\left\lbrace \vd^{(m)}  \right\rbrace_{m=1,\ldots,n}$ with high value stands for the image $\mathcal{I}^{(m)}$ where the most expressive changes take place.

%The time points with highest values of $\vd(m)$ represent the images for which the most expressive changes take place, where changes here are measured through $\mathbb{L}_2$ energy.

%%%RGN: Seria esta a razão?
In order to obtain an expression for the spatio-temporal fluctuations, let consider the following global matrix $\vD$ of order $n \times uv$:
%Define the  $n\times p$ matrix
\begin{equation}\label{eq_defmatrixD}
 \vD=\left(
 \begin{array}{c}
 vec(\vD^{(1)})^T\\
 \vdots\\
 vec(\vD^{(n)})^T\\
 \end{array}
 \right),
\end{equation}
where $vec(\vD^{(m)})$ is a $uv \times 1$ vector representation, using lexicographic ordering, of the wavelet coefficients regarding the instant $m$.
%%%RGN: esta parte fica redundante, pois já definimos os elementos envolvidos aqui...
% and $p=\#\{k,l\}$ is total number of locations represented by $\vX^{(m)}$, $m=1,\ldots,n$. 
\textcolor{red}{(precisa mesmo estar transposto? E se definir como $1 \times uv$?)}

%%%%RGN: Acho que a posicao desta citacao esta errada, nao?
Sparsity \cite{johnstone2009statistical} on wavelet coefficients plays a special role in this formalization.
% here.  
We suppose a handful of coefficients drive the changes given by $\vd$, so that the effective dimension of $\vD$ (number of locations where relevant changes occur), say $s$, is such that $s \ll p$. This can be represented as the following linear model
\begin{equation}\label{E:sparsemodel_d}
\vd=\vD\vbeta+\vxi
\end{equation}
where $\vbeta \in \mathbbm{R}^{uv}$ is sparse, i.e., it has $(uv - s)$ null elements, and $\vxi^{(d)} \in \mathbbm{R}^{n}$ is a random vector. \textcolor{red}{(existe esse $(d)$ no $\xi$ mesmo? Como $\beta$ e $\xi$ são obtidos?)} % of errors
%some $n\times 1$ random vector of errors.

%%%RGN: vamos trocar $s_d$ por $s$? a adicao do d nao faz muita diferenca.

In order to identify spatio-temporal changes, we employ the concept of ultra-high dimensional correlation screening \cite{fan2020statistical} discussed in Section~\ref{section_theroy}.
%as follows. 
For each local \textcolor{red}{squared mean deviation} time series, given by individual elements of $\vD^{(m)}$ across $m=1,\ldots,n$, consider the absolute value of its Pearson correlation with the overall squared mean deviations, given by $\vd$:
\begin{equation*}\label{def_Rkld}
R_{kl}= |\corr \left( \vD_{kl}, \vd \right)|,
\end{equation*}
where $\vD_{kl} = \left\lbrace D_{kl}^{(1)},\ldots,D_{kl}^{(n)} \right\rbrace$ is the time series of \textcolor{red}{squared mean deviations} of wavelet coefficients at position $(k,l)$.
% the two-dimensional index $\{k,l\}$.

%%%RGN: este trecho acima (...where $\vD_{k,l}=(D_{k,l}(1)) pode ser omitido, pois ja definimos quem é D_kl antes da equacao 2. Ok?

\textcolor{magenta}{RGN: Nos destaques em vermelho que fiz acima, é para chamar atenćão que nao se trata de uma squared mean deviation e sim uma squered deviation, certo?}

@@

Consequently, rises the matrix $\vR$ from the elements $R_{kl}$ assigned to each $(k,l) \in \mathcal{S}$.% which contain the ultra-high dimension correlations.
%
%We have a matrix $\vR=[R_{k,l}]$ of correlations of ultra-high dimension. 
%Define the set of {\it important} indices for changes in images with respect to $\bar{\mathcal I}$ as $\mathcal{M}^{*}=\{(k,l): \textit{changes in } \{\mathcal{I}^{(m)}\}_{m=1}^m \textit{ with respect to}$ $\bar{\mathcal{I}}$ \textit{are affected by changes in location corresponding to index} $(k,l)$ $\textit{in such images}\}$.  This set coincides with the non-zero vectorized one-dimensional indices for the sparse representation of $\vbeta$ in (\ref{E:sparsemodel_d}).

Defining a mapping of \textit{important} indices for changes over the image series with respect to $\overline{\mathcal I}$ as $\mathcal{M}^{\star} \subseteq \mathcal{S}$ where \textit{changes in $\{\mathcal{I}^{(m)}\}_{m=1,\ldots,n}$ with respect to $\overline{\mathcal{I}}$ are affected by changes in the images}.
%
Such mapping, when re-written using lexicographic order as adopted to express the columns of $\vR$ (Eq.~\ref{eq_defmatrixD}), coincides with the non-zero components of $\vbeta$ in Equation~\ref{E:sparsemodel_d}.

%$\mathcal{M}^{\star}=\{(k,l) \in \mathcal{S}: \textit{changes in } \{\mathcal{I}^{(m)}\}_{m=1}^m \textit{ with respect to}$ $\bar{\mathcal{I}}$ \textit{are affected by changes in location corresponding to index} $(k,l)$ $\textit{in such images}\}$.  
%This set coincides with the non-zero vectorized one-dimensional indices for the sparse representation of $\vbeta$ in (\ref{E:sparsemodel_d}).

An empirical mapping of change locations may be stated by:
\begin{equation}
\mathcal{M}_{\tau} = \{(k,l) \in \mathcal{S} : |R_{kl}|>\tau\},
\label{E:def_Mtaud}
\end{equation}
where $\tau \in mathbbm{R}_{+}^{*}$ is a convenient threshold value \textcolor{blue}{defined as function of $n$ and $J$}. 
Under \textcolor{red}{some regularity conditions}, the probability $P(\mathcal{M}_{\tau}\supset\mathcal{M}^{\star}) \rightarrow 1$ as $n\rightarrow\infty$ \cite{fan2020statistical}.
In other words, the empirical set $\mathcal{M}_{\tau}$ has high probability of detecting the correct change locations in $\mathcal{M}^{\star}$ when the number of \textcolor{red}{observations} $n$ is large enough. 
%%%RNG: observations mesmo? ou instats?

%We build the empirical set of indices flagged as corresponding to change locations by
%\begin{equation}
%\mathcal{M}_{\tau}=\{(k,l):|R_{k,l}|>\tau\},
%\label{E:def_Mtaud}
%\end{equation}
%where $\tau_d>0$ is a convenient threshold value, function of $n$ and $J$. Under some regularity conditions, the probability that $\mathcal{M}_{\tau}$ contains its target set satisfies
%\[
%P(\mathcal{M}_{\tau}\supset\mathcal{M}^{*})\rightarrow 1,
%\]
%as $n\rightarrow\infty$ \cite{fan2020statistical}, where $P$ denotes a probability measure. In other words, the empirical set $\mathcal{M}_{\tau}$ has high probability of detecting the correct change locations in $\mathcal{M}^{*}$ when the number of observations $n$ is large.

{\color{blue}
RGN: Vamos omitir este trecho abaixo por um instante e depois retomamos? Por enquanto parece faltar uma ligacao clara entreos elementos

Further geometrical motivation for our proposal is given as follows. As defined by (\ref{E:eq_defdm}), we expect $\vd$ to be a vector with some few high values, say $s_d$, and $n-s_d$ smaller values. This segregates the multi-temporal images, since the former time points identify the images in which significant changes occur, while the latter indices identify time points with no major changes. Consider $U>L>0$ such that the $s_d$ highest values of $\vd$ are larger than $U$, and the $n-s_d$ smallest values of $\vd$ are smaller than $L$. We also take $\delta=U-L$. The indices defined by  (\ref{E:def_Mtaud}) are such that   
\[
\frac{<\vD_{k,l},\vd>}{\|\vD_{k,l}\|_2\|\vd\|_2}>\tau,
\]
i.e., such that  $\sum_{m=1}^nD_{k,l}^{(m)}\vd(m)>\tau\|\vD_{k,l}\|_2\|\vd\|_2$. This can be rewritten as
\[
\left|\sum_{m:\vd(m)>U} D_{k,l}^{(m)}\right|-\left|\sum_{m:\vd(m)<L} D_{k,l}^{(m)}\right|>\Delta,
\]
for some arbitrary $\Delta>>0$ (which can be a function of $n$ and $J$). Thence, when we employ correlation screening we select the two-dimensional wavelet indices which have the closest empirical directions to the vector of image temporal changes. Thus we are performing a truly spatio-temporal change detection in a single procedure.
}

@@

\subfigure[Ground truth change/non-change samples]{\includegraphics[width=0.23\textwidth]{../../qgis/maps/Samples.pdf}\label{figImgSentinelROIs}}
